Enhancement of SDR in Thessaloniki

### 2024-02-22 GHI_enh_04_investigate.tex
Commit 2024-02-22 12:14
Commit 2024-02-22 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-22}

@@

lmD: 1.71458 +/- 0.1322584

lmY: 1.714601 +/- 0.1322612

Arima: 1.7152 0.1817 9.4404 0

@@

lmD: 1.015311 +/- 0.173386

lmY: 1.015342 +/- 0.1733898

Arima: 1.1004 0.255 4.3146 0

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

@@

lmD: 605.1187 +/- 96.27827

lmY: 605.1308 +/- 96.28033

Arima: 605.7835 145.2351 4.1711 0

@@

lmD: 0.002984713 +/- 0.0002850018

lmY: 0.00298475 +/- 0.0002850079

Arima: 0.003 4e-04 7.7371 0

@@

lmD: 0.001565283 +/- 0.0003220401

lmY: 0.001565348 +/- 0.000322047

Arima: 0.0018 5e-04 3.3956 7e-04

lmD: -0.1672102 +/- 0.1436958

lmY: -0.1672003 +/- 0.1436989

@@

lmD: 0.9735636 +/- 0.1446246

lmY: 0.9735884 +/- 0.1446277

Arima: 1.0386 0.2143 4.8455 0

@@

lmD: 0.7131394 +/- 0.1236589

lmY: 0.7131522 +/- 0.1236614

Arima: 0.7132 0.1476 4.8325 0

@@

lmD: 0.1205603 +/- 0.04472432

lmY: 0.1205635 +/- 0.04472525

Arima: 0.1206 0.0487 2.4752 0.0133

@@

lmD: 0.5126011 +/- 0.05584138

lmY: 0.5126089 +/- 0.05584254

Arima: 0.5126 0.0703 7.2901 0

@@

lmD: 28.03241 +/- 3.452126

lmY: 28.0328 +/- 3.452198

Arima: 28.0362 4.3653 6.4225 0

@@

lmD: 0.001091243 +/- 0.0001452364

lmY: 0.001091258 +/- 0.0001452394

Arima: 0.0011 2e-04 6.6404 0

@@

lmD: 0.0002586606 +/- 6.142941e-05

lmY: 0.0002586644 +/- 6.143069e-05

Arima: 3e-04 1e-04 3.7461 2e-04

@@

lmD: 0.03561979 +/- 0.004001997

lmY: 0.03562032 +/- 0.004002081

Arima: 0.0356 0.0048 7.3697 0

@@

lmD: -0.1184401 +/- 0.3426654

lmY: -0.1183983 +/- 0.3426728

Arima: -0.1021 0.5303 -0.1925 0.8473

@@

lmD: -0.2498159 +/- 0.2873017

lmY: -0.2497925 +/- 0.287308

Arima: -0.249 0.4778 -0.5212 0.6022

@@

lmD: 4.678815 +/- 4.938622

lmY: 4.679265 +/- 4.938728

Arima: 4.6804 5.0982 0.9181 0.3586

@@

lmD: 0.0002750923 +/- 0.0002421161

lmY: 0.0002751196 +/- 0.0002421213

Arima: 3e-04 3e-04 1.0722 0.2836

@@

lmD: 0.0001464247 +/- 0.0001495252

lmY: 0.0001464348 +/- 0.0001495284

Arima: 1e-04 2e-04 0.8844 0.3765

@@

lmD: 0.007036274 +/- 0.006116865

lmY: 0.007036819 +/- 0.006116997

Arima: 0.007 0.0063 1.1208 0.2624

@@

@@

\begin{verbatim}
2024-01-22 08:48:56.1 athan@sagan GHI_enh_04_investigate.R 0.252639 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-22}

@@

lmD: 1.608404 +/- 0.1098661

lmY: 1.608426 +/- 0.1098682

Arima: 1.6087 0.1487 10.8185 0

@@

lmD: 1.06616 +/- 0.1703576

lmY: 1.066188 +/- 0.1703608

Arima: 1.1439 0.255 4.4864 0

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

lmD: 499.5958 +/- 96.35149

lmY: 499.601 +/- 96.35332

Arima: 500.7839 150.1232 3.3358 9e-04

@@

lmD: 0.003319458 +/- 0.0002745369

lmY: 0.003319501 +/- 0.0002745421

Arima: 0.0033 4e-04 9.0564 0

@@

lmD: 0.001746196 +/- 0.0003178251

lmY: 0.001746269 +/- 0.0003178311

Arima: 0.0019 5e-04 3.7071 2e-04

lmD: 0.2020422 +/- 0.1403033

lmY: 0.2020754 +/- 0.140306

@@

lmD: 0.9305909 +/- 0.1460762

lmY: 0.9306112 +/- 0.146079

Arima: 1.0003 0.2219 4.5077 0

@@

lmD: 0.8634408 +/- 0.1045511

lmY: 0.8634567 +/- 0.1045531

Arima: 0.8634 0.1212 7.1257 0

@@

lmD: 0.1926088 +/- 0.038164

lmY: 0.1926139 +/- 0.03816473

Arima: 0.1926 0.0403 4.7782 0

@@

lmD: 0.5100905 +/- 0.04695669

lmY: 0.5100995 +/- 0.04695759

Arima: 0.5101 0.0557 9.1553 0

@@

lmD: 25.65919 +/- 2.576134

lmY: 25.65971 +/- 2.576183

Arima: 25.6594 3.1045 8.2652 0

@@

lmD: 0.001358275 +/- 0.0001381135

lmY: 0.001358294 +/- 0.0001381161

Arima: 0.0014 2e-04 8.5635 0

@@

lmD: 0.0003544276 +/- 6.15321e-05

lmY: 0.0003544331 +/- 6.153328e-05

Arima: 4e-04 1e-04 5.1881 0

@@

lmD: 0.03803985 +/- 0.003667512

lmY: 0.03804065 +/- 0.003667582

Arima: 0.038 0.0043 8.9476 0

@@

lmD: 0.2175113 +/- 0.2519978

lmY: 0.217552 +/- 0.2520021

Arima: 0.2071 0.368 0.5628 0.5736

@@

lmD: 0.1126483 +/- 0.193195

lmY: 0.112674 +/- 0.1931983

Arima: 0.0865 0.3384 0.2558 0.7981

@@

lmD: 6.106963 +/- 4.268209

lmY: 6.107414 +/- 4.268282

Arima: 6.107 4.3537 1.4027 0.1607

@@

lmD: 0.0004829553 +/- 0.0002839705

lmY: 0.0004829612 +/- 0.0002839754

Arima: 5e-04 3e-04 1.492 0.1357

@@

lmD: 0.000372236 +/- 0.0002233382

lmY: 0.0003722343 +/- 0.0002233421

Arima: 4e-04 3e-04 1.3298 0.1836

@@

lmD: 0.008401207 +/- 0.005558251

lmY: 0.008401691 +/- 0.005558346

Arima: 0.0084 0.0058 1.453 0.1462

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-10} \end{center}

\begin{verbatim}
Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
 <int>        <num>      <num>       <num>       <num>          <num>
\end{verbatim}

1: 481 257.3195 8.350655 267.7489 242.6236 260.3138
2: 971 216.5679 16.495293 235.1144 193.4734 217.7960
3: 2241 227.5736 20.457901 258.0261 193.1068 229.0391
4: 4773 271.5252 11.060322 283.9255 252.6598 271.0824
5: 5117 262.1138 11.248980 274.8783 238.8148 264.6210
6: 6541 253.6101 10.607348 267.7551 234.0414 257.8234
7: 6845 258.8941 14.521709 279.3143 236.2212 259.3578
8: 7467 242.4683 10.808965 255.5432 223.2814 245.7159
9: 9457 241.5889 17.780983 262.0485 217.5930 241.8318
10: 9969 252.6750 12.743428 268.5044 227.0751 256.7234
11: 10165 234.4787 24.636237 272.8474 192.0395 234.9695
12: 11649 240.6856 13.273652 256.0748 217.2753 242.5054
13: 13153 226.7698 13.156939 245.9949 205.9152 227.1448
14: 13443 267.3652 17.692463 297.1763 242.8280 265.7668
15: 15895 249.5382 8.105678 260.5660 235.4649 251.6262
16: 16137 296.0602 11.066762 309.3942 275.7864 297.5333
17: 16171 269.2776 29.202926 309.5713 219.8781 268.9006
18: 16895 254.6044 15.235006 274.4095 225.2859 258.0783
19: 17643 253.1900 13.469979 268.8240 229.1515 252.6631
20: 20345 226.6557 15.490955 243.2169 201.2967 230.7191
21: 21735 284.9456 11.383299 294.4455 266.5703 290.7959
22: 21817 290.7313 11.694535 302.3524 269.8491 293.7271
23: 22165 197.8942 8.745153 210.3744 187.2505 195.5802
24: 22413 271.7703 11.120987 287.8414 254.3186 272.3344
25: 23611 228.9324 11.456181 244.7993 211.1329 229.0438
26: 23891 199.6014 7.185312 210.5290 190.3904 197.4787
27: 25719 214.0681 12.946659 234.4364 194.3404 213.3949
28: 25997 238.5985 13.424769 258.7934 212.3301 238.1350
29: 26285 227.0978 13.456321 248.0932 206.5112 230.1962
30: 26801 253.3993 10.784431 269.0709 235.7569 253.5561
31: 30515 240.4971 13.310081 260.6187 220.6540 242.2806
32: 32341 272.3105 11.410122 283.1927 253.4763 278.5194
33: 32401 305.1635 12.743889 323.8292 284.4144 304.5790
34: 32773 309.3578 10.040387 321.8635 289.3885 311.7055
35: 32961 232.4638 11.267541 245.9080 211.7075 232.6364
36: 33451 225.2788 13.751736 241.9490 201.3797 228.0213
37: 34245 207.9986 16.032702 234.4686 182.6589 210.3605
38: 34523 234.0512 9.322204 246.0256 216.5182 236.1390
39: 36351 218.4261 13.432350 235.0774 197.6608 219.5851
40: 38177 266.8840 13.588883 287.9246 247.9963 265.6052
41: 39591 228.1790 17.191522 247.5159 198.1167 231.1033
42: 40373 311.4466 14.864073 326.7722 286.0813 314.2091
43: 42061 248.7708 20.245299 276.4848 212.5114 253.7164
44: 42973 252.3753 14.880182 271.7679 228.6148 254.1153
45: 44053 244.8663 10.681053 254.4108 224.9672 250.5007
46: 44557 216.6079 18.711766 246.4339 189.0774 214.8244
47: 45027 265.2793 13.305152 278.2774 242.9361 268.8201
48: 46959 246.3336 13.453849 262.4803 222.0861 247.0723
49: 49635 211.1405 12.624785 227.5580 185.0832 213.3587
50: 50495 262.2053 13.934278 277.6889 234.1425 269.4443
51: 50605 249.1680 14.188662 267.4369 224.7586 254.9338
52: 52523 227.7282 20.116051 253.4785 199.4729 226.2721
53: 53139 344.2763 7.339423 354.4374 333.1648 345.1473
54: 56531 275.6256 11.625398 293.1797 258.6227 279.5499
Group0 wattGLB.mean wattGLB.SD wattGLB.max wattGLB.min wattGLB.median
wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
1: 2315.875 9 0.012658526 0.007336238 0.02424117 3.618639e-03
2: 2815.383 13 0.047619711 0.021833954 0.08294003 2.255959e-02
3: 3868.751 17 0.039832241 0.017813047 0.06850870 9.280731e-03
4: 2986.777 11 0.020651085 0.008641277 0.03082640 8.954612e-04
5: 2883.252 11 0.038727945 0.016111091 0.05646997 5.673899e-03
6: 3804.152 15 0.024133423 0.015218137 0.04713257 2.270427e-03
7: 3106.729 12 0.024471454 0.005111052 0.03085490 1.271853e-02
8: 2424.683 10 0.037730781 0.010797752 0.05477434 2.295391e-02
9: 3140.655 13 0.026700651 0.017716174 0.05521067 3.520107e-03
10: 3284.775 13 0.021796120 0.016940071 0.04437075 9.246931e-04
11: 5627.489 24 0.010556456 0.004473778 0.01870079 1.562197e-04
12: 2647.541 11 0.029061085 0.011690478 0.04044334 5.334540e-03
13: 2267.698 10 0.020102389 0.009460425 0.03143787 1.302508e-03
14: 3475.748 13 0.034180747 0.029177954 0.08087082 5.747693e-03
15: 2245.844 9 0.031944825 0.015093392 0.05579390 1.868089e-03
16: 2960.602 10 0.024513994 0.011193488 0.03640057 7.469758e-04
17: 7001.218 26 0.019012780 0.010888190 0.03634797 2.224907e-04
18: 4073.670 16 0.031447300 0.015400785 0.05138621 5.572228e-03
19: 3291.470 13 0.018391577 0.009547554 0.03248679 4.422927e-05
20: 2493.212 11 0.037911399 0.024767963 0.06725911 1.875988e-04
21: 2849.456 10 0.023801910 0.015583707 0.04685870 2.065899e-03
22: 2907.313 10 0.033181155 0.012452456 0.05072824 1.471443e-02
23: 1781.048 9 0.041713910 0.010811978 0.06207495 2.938039e-02
24: 2717.703 10 0.007545367 0.003968287 0.01339272 1.924395e-03
25: 2289.324 10 0.026299708 0.005504021 0.03510600 1.631896e-02
26: 1996.014 10 0.038398619 0.024925074 0.07789760 1.072219e-02
27: 3211.022 15 0.024096160 0.013027169 0.04707513 3.168538e-03
28: 2624.583 11 0.043034541 0.016692047 0.05948743 2.531670e-03
29: 2270.978 10 0.028007669 0.015535227 0.04761875 3.593981e-04
30: 3800.990 15 0.031491054 0.018805811 0.05927515 2.584543e-04
31: 2404.971 10 0.038589789 0.010968345 0.05515072 1.995441e-02
32: 2450.794 9 0.018450798 0.013828299 0.04170371 1.879353e-03
33: 3661.962 12 0.010887983 0.004505853 0.01949511 2.646608e-03
34: 3402.936 11 0.030439037 0.011510021 0.04467660 6.627475e-03
35: 2557.102 11 0.028062706 0.013370819 0.05219082 1.580210e-03
36: 2703.345 12 0.036161296 0.013891987 0.05672386 8.752650e-03
37: 3535.976 17 0.022004659 0.010721158 0.04355565 1.232982e-03
38: 2106.460 9 0.029267500 0.012383610 0.05493501 1.369300e-02
39: 2402.687 11 0.019759475 0.012609945 0.03856265 1.773580e-03
40: 2401.956 9 0.016632251 0.013926082 0.03925770 9.912776e-04
41: 3422.686 15 0.029600589 0.014457621 0.04591226 2.056735e-03
42: 4360.252 14 0.019192384 0.012672902 0.04222100 1.143358e-03
43: 4726.645 19 0.022230155 0.011242035 0.04245011 5.084744e-04
44: 2523.753 10 0.040388316 0.012871856 0.05338784 1.545235e-02
45: 2203.796 9 0.037599517 0.024501144 0.07546839 3.286317e-03
46: 4332.159 20 0.025563708 0.018461184 0.06292646 1.748176e-04
47: 2918.073 11 0.029903082 0.014946483 0.05388691 1.126394e-02
48: 2956.003 12 0.026969021 0.009248109 0.03677788 5.856216e-03
49: 2744.826 13 0.038178239 0.020137012 0.07843259 1.235585e-02
50: 3408.669 13 0.034775401 0.020270629 0.06542295 8.675716e-04
51: 2491.680 10 0.040929889 0.025743183 0.07423877 3.238012e-03
52: 3415.924 15 0.033089620 0.022677872 0.07868768 1.837827e-03
53: 5164.145 15 0.023156220 0.011315598 0.04155787 4.477347e-03
54: 3031.882 11 0.033064675 0.009660209 0.04996016 1.510975e-02
wattGLB.sum wattGLB.N GLB\_ench.mean GLB\_ench.SD GLB\_ench.max GLB\_ench.min
GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
1: 0.015258046 0.11392673 9 3.199036 1.8480448
2: 0.039096006 0.61905624 13 9.966257 4.8884446
3: 0.043623325 0.67714809 17 8.883353 4.3646547
4: 0.022923458 0.22716194 11 5.454028 2.2964250
5: 0.038872608 0.42600739 11 9.720812 3.9778306
6: 0.026109729 0.36200134 15 5.863463 3.6771214
7: 0.026478712 0.29365744 12 6.198542 1.3979056
8: 0.039026838 0.37730781 10 8.789569 2.4734154
9: 0.028149166 0.34710846 13 6.393541 4.3927825
10: 0.025010146 0.28334956 13 5.325565 4.1401913
11: 0.011501331 0.25335495 24 2.385627 0.9033321
12: 0.035082242 0.31967194 11 6.842998 2.8138916
13: 0.021310344 0.20102389 10 4.546239 2.2560872
14: 0.015261181 0.44434972 13 9.049197 7.9546905
15: 0.028532127 0.28750343 9 7.616027 3.4449100
16: 0.026141419 0.24513994 10 7.072265 3.2745393
17: 0.017372697 0.49433229 26 5.177275 3.2101952
18: 0.036315304 0.50315680 16 7.653078 3.7272740
19: 0.021240929 0.23909050 13 4.597832 2.4288289
20: 0.039578716 0.41702539 11 8.430668 5.5901279
21: 0.021613611 0.23801910 10 6.622547 4.3609825
22: 0.033304814 0.33181155 10 9.354052 3.5886059
23: 0.037862781 0.37542519 9 7.871330 1.8081641
24: 0.007193847 0.07545367 10 2.045319 1.0756519
25: 0.026281327 0.26299708 10 5.901763 1.4188436
26: 0.030018550 0.38398619 10 7.177111 4.3189650
27: 0.021968899 0.36144240 15 4.866735 2.3725309
28: 0.050770058 0.47337995 11 9.902114 3.8759116
29: 0.029454867 0.28007669 10 6.263638 3.5362813
30: 0.031495092 0.47236580 15 7.487870 4.2009478
31: 0.039377360 0.38589789 10 8.984041 2.7993517
32: 0.014690505 0.16605718 9 4.963055 3.7497745
33: 0.011258487 0.13065580 12 3.282424 1.3951637
34: 0.030019287 0.33482940 11 9.089175 3.3620941
35: 0.028369249 0.30868976 11 6.244589 2.8426525
36: 0.037457676 0.43393555 12 7.859623 3.0925107
37: 0.020304850 0.37407920 17 4.373601 1.9308509
38: 0.029622972 0.26340750 9 6.627341 2.6671677
39: 0.024055070 0.21735423 11 4.320715 2.7985120
40: 0.012158590 0.14969026 9 4.475643 3.8461418
41: 0.031475748 0.44400884 15 6.595177 3.3311668
42: 0.017107832 0.26869337 14 5.895968 3.9687884
43: 0.021184023 0.42237294 19 5.390649 2.7084635
44: 0.046369850 0.40388316 10 9.911890 3.4559727
45: 0.037114103 0.33839565 9 8.854696 5.7971486
46: 0.020396835 0.51127416 20 5.116160 3.2912175
47: 0.034581387 0.32893390 11 7.742948 3.9356336
48: 0.028914602 0.32362825 12 6.493560 2.2810668
49: 0.040038173 0.49631711 13 7.640835 3.7885766
50: 0.035518569 0.45208022 13 8.732851 5.0956093
51: 0.037655078 0.40929889 10 9.832733 6.3377317
52: 0.026555134 0.49634430 15 7.477650 5.3627709
53: 0.024525322 0.34734329 15 7.689821 3.5802888
54: 0.033550143 0.36371142 11 8.781796 2.4711802
GLB\_ench.median GLB\_ench.sum GLB\_ench.N GLB\_diff.mean GLB\_diff.SD
GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
1: 6.160961 0.95393626 3.732131 28.79133 9 76.31201
2: 17.875093 4.42961403 7.645469 129.56134 13 76.90457
3: 16.393935 1.77569262 9.238884 151.01700 17 76.27771
4: 8.419473 0.25401677 6.006594 59.99431 11 73.20135
5: 14.008714 1.53057138 10.082840 106.92893 11 75.55524
6: 11.550150 0.60022134 5.955268 87.95195 15 77.03026
7: 8.093370 3.14079477 6.554798 74.38251 12 75.58466
8: 12.701306 5.72706736 8.699920 87.89569 10 74.99706
9: 13.415155 0.78688284 6.620988 83.11603 13 76.83387
10: 11.034378 0.20978078 5.844482 69.23234 13 74.74039
11: 3.712330 0.04261748 2.578156 57.25504 24 75.03040
12: 9.744155 1.15291380 8.043454 75.27298 11 74.93893
13: 7.391575 0.26785722 4.692944 45.46239 10 76.44427
14: 22.234745 1.38772473 3.857838 117.63956 13 76.49536
15: 12.860788 0.48035878 7.228265 68.54425 9 76.02615
16: 10.584420 0.22778327 7.720153 70.72265 10 73.10869
17: 10.565255 0.04890994 4.814865 134.60916 26 74.37201
18: 12.601320 1.48118995 8.964507 122.44924 16 74.22174
19: 8.391113 0.01013476 5.350149 59.77182 13 77.00104
20: 15.035396 0.03775594 8.501772 92.73735 11 75.74552
21: 13.123121 0.60704073 6.036769 66.22547 10 73.15433
22: 14.535052 3.91309767 9.143830 93.54052 10 72.96694
23: 10.944203 5.58221547 7.454849 70.84197 9 77.22327
24: 3.683893 0.49514869 2.007895 20.45319 10 74.61690
25: 8.247916 3.39014619 5.856710 59.01763 10 76.00182
26: 13.759151 2.23338608 5.886701 71.77111 10 77.14195
27: 8.737290 0.72729942 4.669355 73.00103 15 76.73547
28: 13.201156 0.53619218 11.641778 108.92325 11 75.18558
29: 10.690524 0.07473518 6.306326 62.63638 10 76.51308
30: 13.192533 0.06952456 7.851910 112.31806 15 76.89333
31: 13.084696 4.81038628 9.002430 89.84041 10 77.07601
32: 11.150283 0.47547802 3.875148 44.66750 9 74.25991
33: 6.192366 0.84981708 3.460090 39.38908 12 72.97619
34: 13.124351 2.09778460 8.620152 99.98092 11 74.32935
35: 11.203243 0.38790970 6.417657 68.69048 11 76.91713
36: 12.228722 2.07816265 8.223374 94.31548 12 76.85870
37: 7.995524 0.26755568 4.026333 74.35122 17 76.52836
38: 11.923298 2.92473441 6.531802 59.64607 9 75.28093
39: 8.517587 0.35569821 5.068282 47.52786 11 76.47527
40: 10.876280 0.24558977 3.190591 40.28079 9 74.58380
41: 10.502950 0.50748250 7.492738 98.92766 15 75.66150
42: 13.107754 0.37304609 5.063451 82.54355 14 74.07967
43: 10.331708 0.14002949 5.300350 102.42234 19 74.44621
44: 13.662964 3.47887935 11.598532 99.11890 10 76.50848
45: 17.810858 0.82052822 8.998589 79.69227 9 74.80061
46: 11.193598 0.04225977 4.197251 102.32320 20 76.14464
47: 14.066980 2.74402614 8.666315 85.17243 11 75.29915
48: 9.266976 1.29301233 6.787583 77.92272 12 74.61536
49: 14.575181 2.75979485 7.672405 99.33086 13 76.56101
50: 16.345143 0.23581784 8.914622 113.52706 13 76.09532
51: 18.482095 0.83094177 8.743070 98.32733 10 76.66623
52: 18.490645 0.37093385 5.889783 112.16475 15 76.51321
53: 13.293183 1.57986595 8.373120 115.34731 15 72.87559
54: 13.332046 4.25076472 9.074488 96.59975 11 74.32984
GLB\_diff.max GLB\_diff.min GLB\_diff.median GLB\_diff.sum GLB\_diff.N SZA.mean
SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date
1: 0.4126326 76.91638 75.71103 76.31079 686.8081 9 1993-11-09 13:44:30
2: 0.6959464 77.97477 75.83039 76.90583 999.7594 13 1994-06-06 04:12:30
3: 0.9063386 77.71007 74.83847 76.27978 1296.7211 17 1995-06-04 16:22:30
4: 0.6229631 74.13993 72.26164 73.20172 805.2148 11 1997-08-08 15:54:30
5: 0.5673775 76.41237 74.70170 75.55404 831.1076 11 1997-10-15 05:58:30
6: 0.5740839 77.93570 76.13869 77.02600 1155.4539 15 1998-12-26 07:16:30
7: 0.6803507 76.62240 74.54679 75.58471 907.0160 12 1999-04-11 15:36:30
8: 0.5720907 75.84711 74.14653 74.99722 749.9706 10 1999-08-23 15:46:30
9: 0.7245096 77.95086 75.71848 76.83336 998.8403 13 2001-03-23 05:34:30
10: 0.6996295 75.81644 73.66070 74.74155 971.6251 13 2001-06-19 04:24:30
11: 1.3259361 77.18335 72.87084 75.03227 1800.7297 24 2001-08-13 04:50:30
12: 0.6225850 75.87690 73.99976 74.93933 824.3282 11 2002-08-12 15:59:30
13: 0.5686156 77.28956 75.59932 76.44415 764.4427 10 2003-09-11 05:15:30
14: 0.5040005 77.27684 75.72395 76.49215 994.4397 13 2003-12-08 07:08:30
15: 0.5157706 76.77922 75.27257 76.02634 684.2354 9 2005-04-20 15:49:30
16: 0.5586641 73.93830 72.27763 73.10918 731.0869 10 2005-05-22 04:40:30
17: 1.3982814 76.64999 72.07998 74.37593 1933.6722 26 2005-05-26 04:23:30
18: 0.8703323 75.59030 72.84829 74.22321 1187.5479 16 2005-07-16 16:15:30
19: 0.5772728 77.89445 76.11577 76.99845 1001.0135 13 2006-01-28 07:00:30
20: 0.6006058 76.64976 74.83889 75.74631 833.2007 11 2007-07-14 16:27:30
21: 0.5525135 73.97468 72.33230 73.15488 731.5433 10 2008-06-01 16:07:30
22: 0.5507165 73.78460 72.14755 72.96751 729.6694 10 2008-06-08 04:35:30
23: 0.5041615 77.95901 76.48627 77.22373 695.0095 9 2008-08-02 04:37:30
24: 0.5335595 75.41114 73.82510 74.61609 746.1690 10 2008-10-06 14:29:30
25: 0.5408238 76.80458 75.19694 76.00253 760.0182 10 2009-06-28 04:21:30
26: 0.5675200 77.98491 76.29791 77.14231 771.4195 10 2009-08-16 16:06:30
27: 0.7946317 77.97640 75.48888 76.73720 1151.0320 15 2010-06-24 04:13:30
28: 0.5979557 76.08580 74.28292 75.18639 827.0413 11 2010-07-07 04:29:30
29: 0.5684890 77.35819 75.66832 76.51296 765.1308 10 2010-09-11 05:15:30
30: 0.6890233 77.97693 75.82008 76.89015 1153.4000 15 2011-02-04 06:51:30
31: 0.5503702 77.89480 76.25879 77.07548 770.7601 10 2013-03-12 05:53:30
32: 0.4981402 74.98817 73.53302 74.25942 668.3392 9 2013-09-26 14:46:30
33: 0.6382201 73.95156 72.00449 72.97502 875.7143 12 2013-10-02 05:56:30
34: 0.5115414 75.10319 73.56088 74.32757 817.6229 11 2014-02-10 14:14:30
35: 0.6246035 77.85876 75.97554 76.91712 846.0884 11 2014-04-05 15:38:30
36: 0.6662228 77.87379 75.84129 76.85944 922.3044 12 2014-05-08 16:08:30
37: 0.9027478 77.95489 75.09468 76.53050 1300.9821 17 2014-07-04 16:31:30
38: 0.5035338 76.01576 74.54485 75.28137 677.5283 9 2014-07-25 16:19:30
39: 0.5904427 77.36402 75.58379 76.47619 841.2280 11 2015-06-26 04:17:30
40: 0.5121475 75.33141 73.83534 74.58411 671.2542 9 2016-05-05 04:46:30
41: 0.8456150 76.98480 74.33769 75.66166 1134.9226 15 2016-08-29 15:37:30
42: 0.6353117 75.07161 73.09742 74.07669 1037.1154 14 2017-02-08 14:08:30
43: 1.0604087 76.14075 72.74900 74.44699 1414.4779 19 2017-08-18 05:00:30
44: 0.5565998 77.33637 75.68185 76.50806 765.0848 10 2018-03-18 15:17:30
45: 0.4979635 75.52724 74.07260 74.80111 673.2055 9 2018-07-13 16:23:30
46: 1.1128487 77.92971 74.35592 76.14570 1522.8929 20 2018-08-20 04:52:30
47: 0.5668083 76.15546 74.44651 75.29792 828.2906 11 2018-10-15 14:17:30
48: 0.6646320 75.62803 73.60037 74.61609 895.3843 12 2019-07-25 16:14:30
49: 0.7312688 77.68680 75.43358 76.56153 995.2931 13 2020-08-18 04:52:30
50: 0.6785496 77.14303 75.05228 76.09383 989.2391 13 2021-03-01 06:16:30
51: 0.5560203 77.49328 75.84048 76.66580 766.6623 10 2021-03-17 15:17:30
52: 0.8424561 77.83192 75.19470 76.51315 1147.6982 15 2021-09-06 05:08:30
53: 0.5012419 73.66846 72.09949 72.87043 1093.1338 15 2021-12-30 07:51:30
54: 0.6155061 75.25692 73.40112 74.33039 817.6283 11 2023-05-12 15:58:30
SZA.SD SZA.max SZA.min SZA.median SZA.sum SZA.N Date

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/sza-15} \end{center}

Empty data.table (0 rows and 30 cols): Group0,wattGLB.mean,wattGLB.SD,wattGLB.max,wattGLB.min,wattGLB.median\ldots{}
Empty data.table (0 rows and 30 cols): Group0,wattGLB.mean,wattGLB.SD,wattGLB.max,wattGLB.min,wattGLB.median\ldots{}
numeric(0)

@@

\begin{verbatim}
2024-02-22 12:06:37.3 athan@tyler GHI_enh_04_investigate.R 0.439034 mins
\end{verbatim}
